Extinction effect

### 2017-12-18 analyses/08-figure-extinction.Rmd
Updated extinction effect (remove Brusatte and Bapst)

```{r, eval = FALSE}
## Slugs (choose one)
slug <- "Beck2014"
# slug <- "Brusatte2014"
# slug <- "Bapst2016"
# slug <- "Wright2017"

@@

## Names of the datasets
slugs <- as.list(c("Beck2014", "Brusatte2014", "Bapst2016", "Wright2017"))

@@

## Plot all the results
pdf("../manuscript/figures/fig-extinction-effect.pdf", width = 12, height = 4)  
multi.plot.extinction(data_list, type = c("age", "epoch"), data.names = unlist(slugs), cols = colours)
dev.off()
```

>>>>

```{r, eval = FALSE}
## Slugs (choose one)
slug <- "Beck2014"
# slug <- "Wright2017"

@@

## Names of the datasets
slugs <- as.list(c("Beck2014", "Wright2017"))

@@

## Plot all the results
pdf("../manuscript/figures/fig-extinction-effect.pdf", width = 8, height = 4)  
multi.plot.extinction(data_list, type = c("age", "epoch"), data.names = unlist(slugs), cols = colours)
dev.off()
```
